tl20-05_berghei_pir_DESEQ

### 2021-09-06 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_berghei_pir_DESEQ.Rmd
SuppInfoName DESEq
berg DESEQ \'apeglm\' package, renv update and stats .csv file save

```{r load_packages}
library('dplyr')
library('readr')
library('readxl')
library('writexl')
library('data.table')
library('tibble')
library('ggplot2')
library('stringr')
library('RColorBrewer')
library('DESeq2')
```

@@

```{r save_stats_df}
write_xlsx(deseq_stats, 
           'SupplementaryInformation_Stats_DESEQ_berghei.xlsx')
```

>>>>

```{r load_packages}
library('dplyr')
library('readr')
library('readxl')
library('writexl')
library('data.table')
library('tibble')
library('ggplot2')
library('stringr')
library('RColorBrewer')
library('DESeq2')
library('apeglm')
```

@@

```{r save_stats_df}
write_xlsx(deseq_stats, 
           'SupplementaryInformation4_Stats_DESEQ_berghei.xlsx')
```
